---
title: "Assignment 1 FML"
author: "Ashrith"
date: "2025-09-07"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

 #I have assigned variable "supermarket_sales" to the supermarket_sales_data dataset
```{r}
supermarket_sales_data <- read.csv("C:/Users/ashri/OneDrive/Desktop/FML/Supermarket sales.csv")
#View(supermarket_sales_data)
head(supermarket_sales_data)
```

```{r}
mode(supermarket_sales_data$Quantity)
```
```{r}
median(supermarket_sales_data$Unit.price)
```
```{r}
mean(supermarket_sales_data$Unit.price)
```
```{r}
max(supermarket_sales_data$Unit.price)
```
```{r}
sd(supermarket_sales_data$Unit.price)
```
These values represent descriptive statistics for a selection of quantitave variables.
The above mentioned values determines mode, median, standard deviation, maximum for the quatitative variables.

```{r}
str(supermarket_sales_data$Payment)
```
These values represent categorical descriptive analysis of variables.



I Summarized descriptive statistics for a selection of quantitative and categorical variables. / Whereas categorical is "Branch"  And quantitative is "Unit.price"
```{r}
summary(supermarket_sales_data$Branch)

```
```{r}
summary(supermarket_sales_data$Unit.price)
```
I have transformed the Unit.price to a new amount by raising it.


```{r}
increased_Unit.price <- sqrt(supermarket_sales_data$Unit.price)
new_price <- (supermarket_sales_data$Unit.price - increased_Unit.price)

```

I generated a scatter plot correlating "Rating" with "Unit.price"
```{r}
x <-supermarket_sales_data$Rating
y <-supermarket_sales_data$Unit.price
plot(x,y, main="scatterplot", xlab = "Rating" , ylab = "Unit.price")


```


The below graphical representation is a histogram.

```{r}

hist(supermarket_sales_data$Unit.price)
```



 The above graphical representation is a histogram 






      This dataset is imported from : https://www.kaggle.com/datasets/aungpyaeap/supermarket-sales
